---
title: "Report"
author: "Adib, Rachit"
date: "January 31, 2016"
output: html_document
---

Design:

1. Each Mapper reads split data from the input files and for each input record in that split it performs sanity.
2. If sanity test pass, then we extract flights for year 2015 with key as "carrier code \t month" and value as "price"
3. The default partioner sends mappers data to reducers based on keys
4. Reducers computes the average price for each carrier and emits key as "carrier code \t month \t count" and value as "average price"
5. Once all the output files from reducers are pushed into S3 bucket, we copy the output from S3 to local machine and combine them into
   single output.
6. Using R script, we extracted the top 10 airlines and plot the graph between average price v/s carrier for each month in year 2015



Conclusion: <br>

Single Threades is the slowest folowed by multi threaded and then on map reduce
It takes O(n) fast median vs O(nlogn) for median

1. There are no flights for any month except January that are active in 2015<br>
2. UA has the maximum average price of 969.09 <br>
3. WN has the minimum average price of 159.35 <br>
4. Ouput does include values for airlines having absurdly high and low (negative) ticket prices, additional check <br>
  can be made but since cutoffs are not provided we are not implementing them. <br>

```{r}
library(ggplot2)

# Read output of Reducer
df <- read.table("finaloutput")

# V1 --> Carrier Code
# V2 --> Month in 2015
# V3 --> Total flights in 2015
# V4 --> Average ticket price in 2015

# Order by V3
o1 <- df[order(df$V3),]

# Get top 10 flights
top10 <- tail(o1, n = 10L)
colnames(top10) <- c("carrier_code", "month", "total_flights", "average_price")

# Convert numeric month to letter abbrevation
top10$month <- month.abb[top10$month]

```


```{r, echo=FALSE}
p <- ggplot(top10, aes(carrier_code, average_price)) + geom_point()
p + facet_grid(. ~ month)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
